Contrast_Model

### 2019-08-27 R Files/ED_Contrast_Graphics.Rmd
Made images

```{r}
## Patient Age and BMI Demographics
PE$Age_range <- cut(PE$Age, breaks = c(0,18,35,110), labels = c("<18", "18-35", ">35"))
PE$BMI_range <- cut(PE$BMI, breaks = c(0,25,40,100), labels = c("<25", "25-40", ">40"))
PE$CT.Type <- factor(PE$CT.Type, levels = c("64SSWoIR", "64SSWithIR", "128SSwIR", "DS_Scanner"))
counts <- as.data.frame(table(PE$Age_range, PE$BMI_range))
names(counts) <- c("Age", "BMI", "n")
counts$Age <- factor(counts$Age, levels = c("<18", "18-35", ">35"))
counts$BMI <- factor(counts$BMI, levels = c("<25", "25-40", ">40"))

@@

Scanner <- PE %>% group_by(CT.Type) %>% summarise(n = n(), Radiation = mean(Contrast.Given),
                                                    Contrast = mean(Contrast.Given))

bar_NumScanner <- ggplot(Scanner, aes(fill = CT.Type, x = CT.Type,
                                       y = n, label = n)) +
                     geom_bar(position = "dodge", stat = "identity", width = 0.5) +
                     geom_text(size = 3, position = position_dodge(0.5), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue" ,"mediumblue" ,"navyblue")) +
                     ylab("Number of Patients") + 
                     xlab("Scanner Type") +
                     #labs(fill = "Age Group") +
                     ggtitle("Number of Patients by Type of Scanner Used")

@@

box_ScannerED <- ggplot(PE, aes(x = CT.Type, y = Contrast.Given, fill = CT.Type)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue", "dodgerblue" ,"mediumblue" ,"navyblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Location") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Location of Admittance")

box_Gender <- ggplot(PE, aes(x = Gender, y = Contrast.Given, fill = Gender)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Gender") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient Gender")

box_Age <- ggplot(PE, aes(x = Age_range, y = Contrast.Given, fill = Age_range)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Gender") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient Gender")

box_BMI <- ggplot(PE, aes(x = BMI_range, y = Contrast.Given, fill = BMI_range)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Gender") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient Gender")

ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_Scanner.jpeg",
       plot = box_ScannerED, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_Gender.jpeg",
       plot = box_Gender, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_Age.jpeg",
       plot = box_Age, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_BMI.jpeg",
       plot = box_BMI, width = 7, height = 5, device = "jpeg")
```

@@

box_Location <- ggplot(PE, aes(x = Location, y = Contrast.Given, fill = Location)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue", "navyblue")) +
                ylab("Contrast (mL)") + 
                xlab("Patient Location") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Patient Location of Admittance")

ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_Scanner.jpeg",
       plot = box_ScannerContrast, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_Location.jpeg",
       plot = box_Location, width = 7, height = 5, device = "jpeg")

>>>>

```{r}
## Patient Age and BMI Demographics
PE$Age_range <- cut(PE$Age, breaks = c(0,18,35,110), labels = c("<18", "18-35", ">35"))
PE$BMI_range <- cut(PE$BMI, breaks = c(0,25,40,100), labels = c("<25", "25-40", ">40"))

PE$CT.Type <- factor(PE$CT.Type, levels = c("64SSWoIR", "64SSWithIR", "128SSwIR", "DS_Scanner"))
PE$CT.Type2 <- ifelse(PE$CT.Type == "64SSWoIR", "64SSwFBP",
                     ifelse(PE$CT.Type == "64SSWithIR", "64SSwSAFIRE",
                            ifelse(PE$CT.Type == "128SSwIR", "128SSwSAFIRE", 
                                   ifelse(PE$CT.Type == "DS_Scanner", "DSwADMIRE", NA))))
PE$CT.Type2 <- factor(PE$CT.Type2, levels = c("64SSwFBP", "64SSwSAFIRE", "128SSwSAFIRE", "DSwADMIRE"))

counts <- as.data.frame(table(PE$Age_range, PE$BMI_range))
names(counts) <- c("Age", "BMI", "n")
counts$Age <- factor(counts$Age, levels = c("<18", "18-35", ">35"))
counts$BMI <- factor(counts$BMI, levels = c("<25", "25-40", ">40"))

@@

Scanner <- PE %>% group_by(CT.Type2) %>% summarise(n = n(), Radiation = mean(Contrast.Given),
                                                    Contrast = mean(Contrast.Given))

bar_NumScanner <- ggplot(Scanner, aes(fill = CT.Type2, x = CT.Type2,
                                       y = n, label = n)) +
                     geom_bar(position = "dodge", stat = "identity", width = 0.5) +
                     geom_text(size = 3, position = position_dodge(0.5), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue" ,"mediumblue" ,"navyblue")) +
                     ylab("Number of Patients") + 
                     xlab("Scanner Type") +
                     #labs(fill = "Age Group") +
                     theme(legend.position = "none") +
                     ggtitle("Number of Patients by Type of Scanner Used")

@@

box_ScannerED <- ggplot(PE, aes(x = CT.Type2, y = Eff.Dose, fill = CT.Type)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue", "dodgerblue" ,"mediumblue" ,"navyblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Location") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Location of Admittance")

box_Gender <- ggplot(PE, aes(x = Gender, y = Eff.Dose, fill = Gender)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Gender") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient Gender")

box_Age <- ggplot(PE, aes(x = Age_range, y = Eff.Dose, fill = Age_range)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Age") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient Age Group")

box_BMI <- ggplot(PE, aes(x = BMI_range, y = Eff.Dose, fill = BMI_range)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient BMI") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient BMI Group")

box_LocationED <- ggplot(PE, aes(x = Location, y = Eff.Dose, fill = Location)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue", "navyblue")) +
                ylab("Effective Dose (mSv)") + 
                xlab("Patient Location") +
                theme(legend.position = "none") +
                ggtitle("Effective Dose Administered by Patient Location")

ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_Scanner.jpeg",
       plot = box_ScannerED, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_Gender.jpeg",
       plot = box_Gender, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_Age.jpeg",
       plot = box_Age, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_BMI.jpeg",
       plot = box_BMI, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Eff_Dose/Box_LocationED.jpeg",
       plot = box_LocationED, width = 7, height = 5, device = "jpeg")
```

@@

box_LocationContrast <- ggplot(PE, aes(x = Location, y = Contrast.Given, fill = Location)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue", "navyblue")) +
                ylab("Contrast (mL)") + 
                xlab("Patient Location") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Patient Location of Admittance")

box_GenderContrast <- ggplot(PE, aes(x = Gender, y = Contrast.Given, fill = Gender)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue")) +
                ylab("Contrast (mL)") + 
                xlab("Patient Gender") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Patient Gender")

box_AgeContrast <- ggplot(PE, aes(x = Age_range, y = Contrast.Given, fill = Age_range)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue")) +
                ylab("Contrast (mL)") + 
                xlab("Patient Age") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Patient Age Group")

box_BMIContrast <- ggplot(PE, aes(x = BMI_range, y = Contrast.Given, fill = BMI_range)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue","dodgerblue", "mediumblue")) +
                ylab("Contrast (mL)") + 
                xlab("Patient BMI") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Patient BMI Group")

ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_Scanner.jpeg",
       plot = box_ScannerContrast, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_Location.jpeg",
       plot = box_LocationContrast, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_Gender.jpeg",
       plot = box_GenderContrast, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_Age.jpeg",
       plot = box_AgeContrast, width = 7, height = 5, device = "jpeg")
ggsave(filename = "EffDose_Contrast_Manuscript/Images/Contrast/Box_BMI.jpeg",
       plot = box_BMIContrast, width = 7, height = 5, device = "jpeg")

### 2019-08-27 R Files/Updated Model/Contrast_Model.Rmd
Made images

```{r}
PE_raw <- read.csv("Data/1st_Set/PE_clean.csv")
PE_short <- PE_raw[,c(4,5,8,9,10,11,12)]
PE_chest <- subset(PE_short, subset = Procedure == "Chest Only")

@@

contrast.aov <- aov(Contrast.Given~CT.Type+BMI_range+Age_range+Gender+Location, data = PE)
TukeyHSD(contrast.aov, which = "CT.Type")
```

>>>>

```{r}
PE_raw <- read.csv("Data/1st_Set/PE_clean.csv")
PE_short <- PE_raw[,c(4,5,7,8,9,10,11,12)]
PE_chest <- subset(PE_short, subset = Procedure == "Chest Only")

@@

contrast.aov <- aov(Contrast.Given~CT.Type+BMI_range+Age_range+Gender+Location, data = PE)
TukeyHSD(contrast.aov)
```
